Simulations of Ballot Polling Risk-Limiting Audits

### 2023-02-19 providence/sections/adversary.tex

%\begin{lemma}
%\Providence is a Strategy-Proof RLA. 
%\end{lemma}
%\begin{proof}
%This property follows from Theorem~\ref{thm:minerva2_is_rla_new} and Lemma~\ref{lemma:markov}. Note that, as described in section \ref{sec:proof}, the proof of the risk-limiting nature of the audit does not rely on round sizes $n_j$ being identical for all values of $k_{j-1}$. 
%\end{proof}
%
To illustrate the practical implication of this property, we consider a toy example: an RLA of a two-candidate contest with margin $0.01$ and risk limit $0.1$. 
Suppose we wish to achieve a conditional stopping probability $0.9$ in each round of the audit. For \Providence, we can compute a new round size for each round based on the previous samples. For \Minerva, however, we would have a predetermined round schedule. We use the default \Minerva round schedule of audit software Arlo \cite{arlo} (used by many states performing an RLA), which is $[x, 2.5x, 6.25x, ...]$; that is, the next marginal round size is $1.5$ times the current one. This multiplier of $1.5$ is known to give, over a wide range of margins, a probability of stopping roughly $0.9$ in the second round if the first round size has probability of stopping $0.9$.

Both the audits of our toy example therefore begin with a first round size of $17,272$ with a $0.9$ probability of stopping, and both will stop in the first round if the sample contains at least $8,725$ ballots for the winner. The audits are identical in the first round, and both numbers of ballots may be computed as described in \cite{usenix_minerva} and integrated into Arlo. We now consider two cases for which the audit proceeds to a second round.

@@

In a less lucky sample, the winner recieves $8,637$ ballots, few more than the loser recieves. In the \Minerva audit, we again have to use a second round size of $43,180$, but now this round size only achieves a $0.727$ probability of stopping, significantly less than the desired $0.9$. Again, the \Providence audit can scale up the second round size according to the first sample and achieve the desired $0.9$ probability of stopping with $58,007$ ballots.

@@

\subsection{Theoretical Properties}
Here we briefly give two interesting theoretical properties of \Providence.

\subsubsection{Efficiency}
In terms of expected ballots sampled, it is easy to see that \Providence dominates EoR \BRAVO in the sense that for any sample for which the EoR \BRAVO stopping condition is met, the \Providence stopping condition is met also.
\begin{lemma}
\label{lem:efficiency}
% For any round schedule %$[n_1, \ldots, n_r]$
For any risk-limit $\alpha \in (0, 1)$, for any margin
and for any round schedule $[n_1, \ldots, n_j]$, 
the \Providence RLA stops before or in the same round as EoR \BRAVO.
\end{lemma}
\begin{proof} Appendix~\ref{sec:proofs}\end{proof}

\subsubsection{Markov-like Stopping Condition}
After $j-1$ rounds, having drawn $n_{j-1}$ cumulative ballots with $k_{j-1}$ cumulative winner ballots, the \Providence stopping condition in round $j$ with size $n_j$ is equivalent to the \Providence stopping condition for a second round where the first round size is $n_1=n_{j-1}$ with $k_1=k_{j-1}$ winner ballots and a second round size $n_2=n_j$. The particular sequence of round sizes and winner ballots found does not affect the \Providence stopping condition; only the previous cumulative round size and number of winner ballots matters. \Minerva does not have this property, but \BRAVO also does.

>>>>

%\begin{lemma}
%\Providence is a Strategy-Proof RLA. 
%\end{lemma}
%\begin{proof}
%This property follows from Theorem~\ref{thm:minerva2_is_rla_new} and Lemma~\ref{lemma:markov}. Note that, as described in section \ref{sec:proof}, the proof of the risk-limiting nature of the audit does not rely on round sizes $n_j$ being identical for all values of $k_{j-1}$. 
%\end{proof}
%
To illustrate the practical implication of this property, we consider a toy example: an RLA of a two-candidate contest with margin $0.01$ and risk limit $0.1$. 
For a conditional stopping probability of $0.9$ in each round of a \Providence audit, we can compute next round sizes based on the current sample. \Minerva, however, would have a predetermined round schedule. We use the default \Minerva round schedule of audit software Arlo: $[x, 2.5x, 6.25x, ...]$; that is, the next marginal round size is $1.5$ times the current one---equivalently, the next total round size is $2.5$ times the current one. This approach is known to give, over a wide range of margins, a conditional probability of stopping roughly $0.9$ in the second round if the first round size was determined for a probability of stopping $0.9$.

Both the audits of our toy example therefore begin with a first round size of $17,272$ with a $0.9$ probability of stopping, and both will stop in the first round if the sample contains at least $8,725$ ballots for the winner. The audits are identical in the first round, and both numbers of ballots may be computed as described in \cite{usenix_minerva} and used by Arlo. We now consider two cases for which the audit proceeds to a second round.

@@

In a less lucky first round sample, the winner recieves $8,637$ ballots, few more than the loser recieves. In the \Minerva audit, we again have to use a second round size of $43,180$, but now this round size only achieves a $0.727$ probability of stopping, significantly less than the desired $0.9$. Again, the \Providence audit can scale up the second round size according to the first sample and achieve the desired $0.9$ probability of stopping with $58,007$ ballots.

@@

\subsection{Theoretical Properties}
Here we present two interesting theoretical properties of \Providence.

\subsubsection{Efficiency}
It is easy to see that, for any sample for which the EoR \BRAVO stopping condition is met, the \Providence stopping condition is also met. This implies that \Providence will never draw more ballots than EoR \BRAVO. 
\begin{lemma}
\label{lem:efficiency}
% For any round schedule %$[n_1, \ldots, n_r]$
For any risk-limit $\alpha \in (0, 1)$, for any margin
and for any round schedule $[n_1, \ldots, n_j]$, 
the \Providence RLA stops before or in the same round as EoR \BRAVO.
\end{lemma}
\begin{proof} Appendix~\ref{sec:proofs}\end{proof}

\subsubsection{Markov-like Stopping Condition}
After $j-1$ rounds, having drawn $n_{j-1}$ cumulative ballots with $k_{j-1}$ cumulative winner ballots, the \Providence stopping condition in round $j$ with size $n_j$ is equivalent to the \Providence stopping condition for a second round where the first round size is $n_1=n_{j-1}$ with $k_1=k_{j-1}$ winner ballots and a second round size $n_2=n_j$. The particular sequence of round sizes and winner ballots does not affect the \Providence stopping condition; only the previous cumulative round size and number of winner ballots matters. \Minerva does not have this property, but \BRAVO also does.

### 2023-02-19 providence/sections/intro.tex

\subsubsection{The Audit Model}
An audit is typically defined as a binary hypothesis test. If the null, $H_0$, is defined as the incorrect outcome hardest to detect (generally a tie, see \cite{Bayesian-RLA}), we have the following definition of an RLA.

@@

Definition \ref{def:RLA} is valid at the end of the RLA, and not at the end of each round. Thus it is not the case that an incorrect election will pass the audit if a sufficient number of rounds is drawn. In fact, the larger a sample, the more accurate the estimate of election correctness can be, and the more the audit will diverge from one that would stop (see the example below). Of course, though, it is possible to declare an incorrect outcome as correct even after drawing a large sample, but a good audit is less likely to make this error.

@@

\npara{\bf Full Hand Count:} It is worth noting here that if election officials do not have a plan for when they will move to a full hand count, and the election outcome is incorrect, at least a fraction $(1-\alpha)$ of the audits will {\em never} stop, and new rounds will continue to be drawn. See Figure \ref{fig:prov-risk} in section \ref{sec:sims} for the results of 10,000 simulations of \Providence on tied elections (risk limit of 0.1, across election margins). Observe that, for each margin studied, more than 90\% of the audits do not stop after 5 rounds. We present two example simulations from among the ones reported to illustrate this idea.

Consider the 2020 US President contest in the state of Texas \cite{MIT-Data-Lab}; candidate Trump won with a total of 5,890,347 votes, and the second highest vote count was that of candidate Biden, who received 5,259,126 votes, for a margin of 0.056614 in the pairwise contest (that is, ignoring the votes received by other candidates). The total number of votes cast in this contest, including invalid votes and votes for other candidates (all termed {\em irrelevant} votes for this pairwise contest), was 11, 315,056. A first round size of 2,217 corresponds to a stopping probability of 0.9 and a risk limit of $\alpha=0.1$ for \Providence (see \cite{usenix_minerva} for a description of how first round size may be computed, \Minerva and \Providence are identical in the first round). The audit stops when the inverse of the \Providence ratio (see section \ref{sec:prov}) is smaller than $\alpha$. We describe two audit simulations using these parameters.

@@

The second simulation assumed a tied election and did not stop at the end of five rounds. 
%The design of the \Providence audit (see section \ref{sec:prov}) ensures that the risk of the first round is no more than 0.9 times the risk limit, and the risk expended in the first round is roughly 0.09. 
Table \ref{tab:toy} lists the round sizes, votes for both candidates and the inverse \Providence ratio after each draw. Each round size was chosen for a conditional stopping probability of 0.9, given that the audit did not stop so far. For example, this corresponds to an approximate probability of 0.09 that the audit stops in the second round (that it does not stop in the first round and stops in the second), and so on. 
\begin{table}[h]
\centering
%\scriptsize
\begin{tabular}{|crrrc|}
\hline
\hline
Round& Cumulative& Trump & Biden & Inverse  \\
 No. & Round Size &  & & Ratio \\
\hline
\hline
1 & 2,217 & 1,111 & 1,079 & 0.256\\
2 & 5,970 & 2,940 & 2,953 & 4.251\\
3 & 16,685 & 8,281 & 8,171 & 3,150 \\
4 & 35,096 & 17,320 & 17,264 & 380,220,376 \\
5 & 76,979 & 37,943 & 37,868 & $2.5e^{+22}$ \\
\hline
\end{tabular}
\caption{A simulation of a \Providence audit of a tied contest when the announced election has a margin of 0.056614, each round size is computed for a conditional stopping probability of $0.9$, and $\alpha=0.1$.}
\label{tab:toy}
\end{table}

@@

\subsection{Gaps in Prior Work and Our Contributions}
Having provided context above, we now describe gaps in our knowledge of audits and describe our contributions. 
\subsubsection{Limitations of \Minerva}
Zag\'{o}rski {\em et al.}  prove that \Minerva \cite{usenix_minerva} is risk-limiting when the number of relevant ballots drawn in each round is pre-determined before any ballots are examined. They do not address the case of a stronger adversary (such as an audit insider) who can determine the size of the next round after knowing what votes are on the ballots sampled thus far. In particular, an open question about \Minerva is whether its RLA proof holds in this case. Can the audit insider increase the audit's error probability beyond its declared risk limit? Or is there no probabilistic adversarial advantage to being able to compute next round sizes after knowing the drawn sample? We do not answer this question, and to our knowledge, it remains open.

Until \Minerva is proven to be risk-limiting to a given risk limit for the adversary who can determine next round size after examining the current sample, it may not be used in audits whose round sizes are not pre-determined. This presents a major limitation, because the stopping probability of the next round is better estimated using information of the sample drawn thus far, but this would not be allowed for \Minerva. The current implementation of \Minerva integrated as an option in Arlo uses a fixed multiplier of the current round size to compute the next round size, thus allowing the first round to be computed as desired, and fixing the next round sizes thereafter\footnote{Note that every draw may contain invalid or irrelevant ballots, and thus the true number of relevant ballots can never be predetermined. However, because this is random, and not controllable by an adversary once the size of the draw is fixed, we assume that differences in the number of ballots average out, and that a fixed draw size is sufficient, though this is not explicitly proven in \cite{usenix_minerva}.}. This could lead to the drawing of too few or too many ballots and greatly constrains audit planning.

@@

\subsubsection{Limitations in Existing Workload Measures}
A major limitation of our understanding of the ballot polling problem as a community is that we use the number of ballots drawn or values proportional to this number \cite{mclaughlin_thesis,bernhard-diss,RI-report} as measures of the workload of an audit. If this were a correct measure of the workload of an audit, we would want to use B2 audits (round size is one) and make decisions about stopping the audit after drawing each ballot, because this leads to the smallest expected number of ballots. As described above, election officials, on the other hand, greatly prefer drawing many ballots at once. From conversations with election officials and staff members of Verified Voting, Brennan Center and Common Cause who have been training election officials to perform RLAs, we estimate that this preference is likely due to the following.

Firstly, each round has an overhead workload as well, including setting up the round and communicating among the various localities involved in conducting the audit (for example, audits of statewide contests involve the drawing of ballots at county offices where the ballots are stored). Secondly, there is an overhead to finding a storage box and unsealing it. For large round sizes, multiple ballots may be drawn at once from a box, and the number of boxes retrieved is smaller than the number of ballots (storage boxes commonly contain many hundreds of ballots each). 
%For smaller round sizes, the number of times a box is retrieved would be roughly identical to the number of ballots drawn, as it is unlikely that a single box will hold multiple ballots from the sample. 
Finally, in the current environment of misinformation, election officials fear a misleading audit sample (falsely indicating that the loser won), preferring to structure audits to reduce the chances of such samples, thus implicitly choosing larger round sizes.

Thus the workload of an audit is not simply a linear (or affine) function of the number of ballots drawn. Relatedly, an optimal round schedule is not completely determined by the expected number of ballots drawn. It depends on other variables as well. The consideration of all these variables is necessary while planning an audit.

@@

The stopping condition for \Minerva does not take into account the sample obtained in previous rounds, and, in \cite{usenix_minerva}, its risk limit is estimated through weighted averages across multiple rounds, assuming that round sizes do not depend on the previous sample. 
%Further, it assumes that the null hypothesis is a tie. 
A far simpler proof is possible for the risk-limiting property of \Providence. 
In particular, the proof does not require an assumption about round sizes.

>>>>

\subsubsection{The Audit Model}
\label{sec:intro-model}
An audit is typically defined as a binary hypothesis test. If the null, $H_0$, is defined as the incorrect outcome hardest to detect (generally a tie, see \cite{Bayesian-RLA}), we have the following definition of an RLA.

@@

Definition \ref{def:RLA} is valid at the end of the RLA, and not at the end of each round. Thus it is not the case that an incorrect election will pass the audit if a sufficient number of rounds is drawn. In fact, the larger a sample, the more accurate the estimate of election correctness can be, and the more the audit will diverge from one that would stop (see the example below). It is possible to declare an incorrect outcome as correct even after drawing a large sample, but a good audit is less likely to make this error.

@@

\npara{\bf Full Hand Count:} It is worth noting here that if election officials do not have a plan for when they will move to a full hand count, and the election outcome is incorrect, at least a fraction $(1-\alpha)$ of the audits will {\em never} stop, and new rounds will continue to be drawn. See Figure \ref{fig:prov-risk} in section \ref{sec:sims} for the results of 10,000 simulations of \Providence on tied elections (risk limit of 0.1, across election margins of 0.05 and larger in the statewide contests for US President in 2020), each simulation stopping after five rounds. Observe that, for each margin studied, more than 90\% of the audits do not stop after five rounds. We present two example simulations from among the ones reported for the state of Texas to illustrate this idea.

A total of 11, 315,056 votes were cast in the 2020 US President contest in the state of Texas \cite{MIT-Data-Lab}; candidate Trump won with 5,890,347 votes, and the second highest vote count was that of candidate Biden, who received 5,259,126 votes, for a margin of 0.0566 in the pairwise contest. A pairwise contest between two candidates treats invalid votes and those received by other candidates as irrelevant to determining which of the two won the pairwise contest. Its {\em margin} is the difference between their vote counts as a fraction of the sum of their votes. Ballot polling audits used to audit government elections (such as \BRAVO, \Minerva and \Providence) audit a multi-candidate contest by conducting multiple audits of the pairwise contests between the winner and every other candidate.

A first round size of 2,217 corresponds to a stopping probability of 0.9 and a risk limit of $\alpha=0.1$ for \Providence (see \cite{usenix_minerva} for a description of how first round size may be computed, \Minerva and \Providence are identical in the first round). The audit stops when the inverse of the \Providence ratio (see section \ref{sec:prov}) is smaller than $\alpha$. We describe two audit simulations using these parameters.

@@

The second simulation assumed a tied election and did not stop at the end of five rounds. 
%The design of the \Providence audit (see section \ref{sec:prov}) ensures that the risk of the first round is no more than 0.9 times the risk limit, and the risk expended in the first round is roughly 0.09. 
Table \ref{tab:toy} lists the cumulative round sizes, cumulative votes for both candidates and the inverse \Providence ratio after each draw. Each round size was chosen for a conditional stopping probability of 0.9, given that the audit did not stop so far. For example, this corresponds to an approximate probability of 0.09 that the audit stops in the second round (that it does not stop in the first round and stops in the second), and so on. 
\begin{table}[h]
\centering
%\scriptsize
\begin{tabular}{|crrrc|}
\hline
\hline
Round& Cumulative& Trump & Biden & Inverse  \\
 No. & Round Size &  & & Ratio \\
\hline
\hline
1 & 2,217 & 1,111 & 1,079 & 0.256\\
2 & 5,970 & 2,940 & 2,953 & 4.251\\
3 & 16,685 & 8,281 & 8,171 & 3,150 \\
4 & 35,096 & 17,320 & 17,264 & 380,220,376 \\
5 & 76,979 & 37,943 & 37,868 & $2.5e^{+22}$ \\
\hline
\end{tabular}
\caption{A simulation of a \Providence audit of a tied contest with an announced margin of 0.0566, and $\alpha=0.1$. Each round size is computed for a conditional stopping probability of $0.9$. The stopping condition is Inverse Ratio < $\alpha$}
\label{tab:toy}
\end{table}

@@

\subsection{Gaps in Prior Work and Our Contributions}
We describe relevant gaps in our knowledge of audits and then describe our contributions. 
\subsubsection{Limitations of \Minerva}
Zag\'{o}rski {\em et al.}  prove that \Minerva \cite{usenix_minerva} is risk-limiting when the number of relevant ballots drawn in each round is pre-determined before any ballots are examined. They do not address the case of a stronger adversary (such as an audit insider) who can determine the size of the next round after knowing what votes are on the ballots sampled thus far. An open question about \Minerva is whether its RLA proof holds in this case. Can the audit insider increase the audit's error probability beyond its declared risk limit? Or is there no probabilistic adversarial advantage to being able to compute next round sizes after knowing the drawn sample? We do not answer this question, and to our knowledge, it remains open.

Until \Minerva is proven to be risk-limiting to a given risk limit for the adversary who can determine next round size after examining the current sample, it may not be used in audits whose round sizes are not pre-determined. This presents a major limitation, because the stopping probability of the next round is better estimated using information of the sample drawn thus far, but this would not be allowed for \Minerva. The current implementation of \Minerva integrated as an option in Arlo uses a fixed multiplier of the current round size to compute the next round size, thus allowing the first round to be computed as desired, and fixing the next round sizes thereafter\footnote{Note that every draw may contain irrelevant ballots, and thus the true number of relevant ballots can never be predetermined. However, because this is random, and not controllable by an adversary once the size of the draw is fixed, we assume that differences in the number of ballots average out, and that a fixed draw size is sufficient, though this is not explicitly proven in \cite{usenix_minerva}.}. This could lead to the drawing of too few or too many ballots and greatly constrains audit planning.

@@

\subsubsection{Limitations in Existing Workload Measures}
A major limitation of our understanding of the ballot polling problem as a community is that we use the number of ballots drawn or values proportional to this number \cite{mclaughlin_thesis,bernhard-diss,RI-report} as measures of the workload of an audit. If this were a correct measure of the workload of an audit, we would want to use B2 audits (round size is one) and make decisions about stopping the audit after drawing each ballot, because this leads to the smallest expected number of ballots. As described in \ref{sec:related}, election officials, on the other hand, greatly prefer drawing many ballots at once. From conversations with election officials and staff members of Verified Voting, Brennan Center and Common Cause who have been training election officials to perform RLAs, we estimate that this preference is likely due to the following.

Firstly, each round has an overhead workload as well, including setting up the round and communicating among the various localities involved in conducting the audit (for example, audits of statewide contests involve the drawing of ballots at county offices where the ballots are stored). Secondly, there is an overhead to finding a storage box and unsealing it. For large round sizes, multiple ballots may be drawn at once from a box, and the number of boxes retrieved is smaller than the number of ballots (storage boxes commonly contain many hundreds of ballots each). 
%For smaller round sizes, the number of times a box is retrieved would be roughly identical to the number of ballots drawn, as it is unlikely that a single box will hold multiple ballots from the sample. 
Finally, in the current environment of misinformation, election officials fear a misleading audit sample (with more votes for an announced losing candidate than the winner), preferring to structure audits to reduce the chances of such samples, thus implicitly choosing larger round sizes.

Thus the workload of an audit is not simply a linear (or affine) function of the number of ballots drawn. Relatedly, an optimal round schedule is not completely determined by the expected number of ballots drawn. It depends on other variables as well, the consideration of which is necessary while planning an audit.

@@

The stopping condition for \Minerva does not take into account the sample obtained in previous rounds, and, in \cite{usenix_minerva}, its risk limit is estimated through weighted averages across multiple rounds, assuming that round sizes do not depend on the previous sample. 
%Further, it assumes that the null hypothesis is a tie. 
Attempting to simplify the proof of \Minerva's risk-limiting property, we were able to define a different audit \Providence. The RLA proof for \Providence does not make an assumption about round sizes.

### 2023-02-19 providence/sections/related.tex

{\bf Ballot Polling RLA Process:} Bernhard provides a good description of the RLA and its assumptions, and also describes the process on the ground \cite{bernhard-sok}.

Election officials typically draw ballots in large round sizes, see for example \cite{va-2022,RI-report}. Note also that, in addition to allowing users to directly enter a round size or choose the expected number of ballots drawn by \BRAVO, Arlo provides choices of stopping probabilities of $0.9$, $0.8$ and $0.7$ (\cite{usenix_minerva} provides estimates of these round sizes for each state in the 2020 US Presidential election, for a $0.9$ probability of stopping; some numbers are in tens and hundreds of thousands of ballots, and thousands of ballots are quite common). For the two audits we attended, election officials chose stopping probabilities of at least $0.9$. We are not aware of any ballot polling RLA performed on ballots cast in a governmental election that drew ballots one at a time (though the stopping condition can be computed one ballot at a time, the ballots are drawn in rounds). \BRAVO hence cannot be used as a B2 audit in these scenarios.

{\bf R2 and B2 Audits and the Classical \BRAVO audit:} A {\em round-by-round (R2)} audit is the general audit, where the decision of whether to draw more ballots or not is taken after drawing a round of ballots. A {\em ballot-by-ballot (B2)} audit is the special case of round size one---when the decision is made after each ballot is drawn. The popular \BRAVO audit requires the smallest expected number of ballots when the announced tally of the election is correct, and stopping decisions are taken a ballot at a time (that is, when it is used as a B2 audit).

For use as an R2 audit, the \BRAVO stopping condition can be applied once at the end of each round (End-of Round (EoR)), or retroactively after each ballot drawn if ballot order is retained (Selection-Ordered (SO)). SO \BRAVO is closer to the original B2 \BRAVO, and requires fewer ballots on average than EoR \BRAVO. But it requires the additional effort of tracking the order of ballots, and should be expected to be inefficient because it does not use the information in the ballots drawn at the end.

%The \BRAVO audit \cite{bravo} is the most popular ballot polling audit. When ballots are sampled one at a time, it is the audit with the smallest expected number of ballots drawn. 
{\bf Newer Ballot Polling Audits:} The \Minerva audit \cite{usenix_minerva,arxiv_athena} does not need ballot order and relies only on sample and round tallies. It was developed for use with large first round sizes, and has been proven to be risk limiting when the round schedule for the audit is fixed before any ballots are drawn. First-round sizes for a stopping probability of $0.9$ when the announced tally is correct have been shown to be smaller than those for EoR and SO \BRAVO for a wide range of margins; simulations \cite{arxiv_athena} support these observations.

@@

{\bf Simulations:} Ballot polling audit simulations provide a means of educating the public and election officials \cite{dice} and understanding audit properties \cite{mclaughlin_thesis,simulations_house, blom_IRV, DBLP:conf/evoteid/HuangRSTV20,bravo}. There is work measuring the amount of time taken to examine a single ballot \cite{RI-report}. 
Simple workload estimates may be obtained by using the number of ballots drawn \cite{bernoulli-ballot-polling}, a more thorough workload estimation model includes the time taken to access individual ballots\cite{bernhard-diss}.

Zag\'{o}rski {\em et al.}  also present first-round simulations demonstrating that \Minerva draws fewer ballots than SO \BRAVO in the first round for large first round sizes when the true tally is as announced. Broadrick {\em et al.} provide further simulations showing that \Minerva requires fewer ballots than EoR and SO \BRAVO over multiple rounds and for smaller stopping probability. As expected, the advantage of \Minerva decreases for smaller stopping probability (smaller round sizes) as it approaches a B2 audit, 
%round schedule (1,1,1,\ldots) 
for which \BRAVO is known to be most efficient.

{\bf Ballot and Batch Comparison Audits:} In a ballot comparison RLA \cite{RLA}, the manual interpretation of each sampled ballot is compared to the corresponding Cast Vote Record (CVR), which is the machine interpretation of the ballot. Ballot comparison RLAs require the fewest ballots of all known RLA approaches, but also require a means of identifying the CVR corresponding to a particular ballot. Not all voting systems record CVRs and their use can present privacy challenges. %A typical approach is to use a ballot serial number on both paper ballot and CVR. When voters vote in precincts, however, serial numbers on ballots can enable the correlation of ballots with voters, and ballots are typically not numbered. Additionally, some voting systems do not record a CVR. One may perform a transitive audit by rescanning unnumbered voted ballots with special scanners which produce CVRs and also print numbers on the ballots as they are scanned. This requires an investment in a sufficiently large number of such printers and in the human effort of rescanning ballots, and is not always feasible. There is recent work on {\em adaptive comparison} RLAs, which relies on scanning only the batches necessary \cite{adaptive-comparison}. In either case, the workload of a transitive ballot comparison audit, measured in hours, would not be simply a linear function the number of ballots drawn, but would include a term which would depend on the total number of ballots rescanned. 
A batch comparison RLA \cite{RI-report} samples batches of ballots (typically, a batch is a storage box of ballots) and compares the manual tally of each sampled batch with the announced tally of that batch. %Thus, while this type of audit does not need CVRs, it does need the publication of the tally of each batch. 
Batch comparison typically requires the sampling of a very large number of ballots, larger than polling audits except for small enough margins. 
%However, the process is most similar to that which election officials already use when they perform fixed-percentage post-election audits, where, for example, 2\% of the batches are manually tallied. (Note that, for an RLA, the number of batches tallied is not fixed; the risk limit is. A smaller number of batches might be sufficient, or a larger number necessary, for an audit with the required risk limit.)

>>>>

\npara{\bf Ballot Polling RLA Process:} Bernhard provides a good description of the RLA and its assumptions, and also describes the process on the ground \cite{bernhard-sok}.

Election officials typically draw ballots in large round sizes, see for example \cite{va-2022,RI-report}. Note also that, in addition to allowing users to directly enter a round size or choose the expected number of ballots drawn by \BRAVO, Arlo provides choices of stopping probabilities of $0.9$, $0.8$ and $0.7$. For the two audits we attended, election officials chose stopping probabilities of at least $0.9$. Estimates of round sizes with stopping probability 0.9 for each state in the 2020 US Presidential election may be found in \cite{usenix_minerva}. Thousands of ballots is quite a common estimate; many estimates are as large as tens and hundreds of thousands of ballots. We are not aware of any ballot polling RLA performed on ballots cast in a governmental election that drew ballots one at a time (though the stopping condition can be computed one ballot at a time, the ballots are drawn in rounds).

\npara{\bf R2 and B2 Audits and the Classical \BRAVO audit:} A {\em round-by-round (R2)} audit is the general audit, where the decision of whether to draw more ballots or not is taken after drawing a round of ballots. A {\em ballot-by-ballot (B2)} audit is the special case of round size one---when the decision is made after each ballot is drawn. The popular \BRAVO audit requires the smallest expected number of ballots when the announced tally of the election is correct, and stopping decisions are taken a ballot at a time (that is, when it is used as a B2 audit). However, \BRAVO cannot be used as a B2 audit in the scenarios described in the previous paragraph.

For use as an R2 audit, the \BRAVO stopping condition can be applied once at the end of each round (End-of Round (EoR)), or retroactively after each ballot drawn if ballot order is retained (Selection-Ordered (SO)). SO \BRAVO is closer to the original B2 \BRAVO, and requires fewer ballots on average than EoR \BRAVO. But it requires the additional effort of tracking the order of ballots, and should be expected to be inefficient because it does not use the information in the ballots drawn towards the end of the round.

%The \BRAVO audit \cite{bravo} is the most popular ballot polling audit. When ballots are sampled one at a time, it is the audit with the smallest expected number of ballots drawn. 
\npara{\bf Newer Ballot Polling Audits:} The \Minerva audit \cite{usenix_minerva,arxiv_athena} does not need ballot order and relies only on sample and round tallies. It was developed for use with large first round sizes, and has been proven to be risk limiting when the round schedule for the audit is fixed before any ballots are drawn. First-round sizes for a stopping probability of $0.9$ when the announced tally is correct have been shown to be smaller than those for EoR and SO \BRAVO for a wide range of margins.

@@

\npara{\bf Simulations:} Ballot polling audit simulations provide a means of educating the public and election officials \cite{dice} and understanding audit properties \cite{mclaughlin_thesis,simulations_house, blom_IRV, DBLP:conf/evoteid/HuangRSTV20,bravo}. There is work measuring the amount of time taken to examine a single ballot \cite{RI-report}. 
Simple workload estimates may be obtained by using the number of ballots drawn \cite{bernoulli-ballot-polling}, a more thorough workload estimation model includes the time taken to access individual ballots\cite{bernhard-diss}.

Zag\'{o}rski {\em et al.}  present first-round simulations demonstrating that \Minerva draws fewer ballots than SO \BRAVO in the first round for large first round sizes when the true tally is as announced. Broadrick {\em et al.} provide further simulations showing that \Minerva requires fewer ballots than EoR and SO \BRAVO over multiple rounds and for smaller stopping probability. As expected, the advantage of \Minerva decreases for smaller stopping probability (smaller round sizes) as it approaches a B2 audit, 
%round schedule (1,1,1,\ldots) 
for which \BRAVO is known to be most efficient.

\npara{\bf Ballot and Batch Comparison Audits:} In a ballot comparison RLA \cite{RLA}, the manual interpretation of each sampled ballot is compared to the corresponding Cast Vote Record (CVR), which is the machine interpretation of the ballot. Ballot comparison RLAs require the fewest ballots of all known RLA approaches, but also require a means of identifying the CVR corresponding to a particular ballot. Not all voting systems record CVRs and their use can present privacy challenges. %A typical approach is to use a ballot serial number on both paper ballot and CVR. When voters vote in precincts, however, serial numbers on ballots can enable the correlation of ballots with voters, and ballots are typically not numbered. Additionally, some voting systems do not record a CVR. One may perform a transitive audit by rescanning unnumbered voted ballots with special scanners which produce CVRs and also print numbers on the ballots as they are scanned. This requires an investment in a sufficiently large number of such printers and in the human effort of rescanning ballots, and is not always feasible. There is recent work on {\em adaptive comparison} RLAs, which relies on scanning only the batches necessary \cite{adaptive-comparison}. In either case, the workload of a transitive ballot comparison audit, measured in hours, would not be simply a linear function the number of ballots drawn, but would include a term which would depend on the total number of ballots rescanned. 
A batch comparison RLA \cite{RI-report} samples batches of ballots (typically, a batch is a storage box of ballots) and compares the manual tally of each sampled batch with the announced tally of that batch. %Thus, while this type of audit does not need CVRs, it does need the publication of the tally of each batch. 
Batch comparison typically requires the sampling of a very large number of ballots, larger than polling audits except for small enough margins. 
%However, the process is most similar to that which election officials already use when they perform fixed-percentage post-election audits, where, for example, 2\% of the batches are manually tallied. (Note that, for an RLA, the number of batches tallied is not fixed; the risk limit is. A smaller number of batches might be sufficient, or a larger number necessary, for an audit with the required risk limit.)
